---
title: "lab6.Rmd"
author: "Bhaven Patel"
date: '`r format(Sys.Date(),format="%A, %B, %d, %Y")`'
output: 
  html_document:
    toc: true
    toc_float: true
    fig_caption: true
    highlights: pygments
    number_sections: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Task 1

## set working directory

```{r}
getwd()
```

# Task 2

## layout() to construct 4 plots in a plotting region

```{r}
layout(matrix(1:4, nr=2,nc=2))
layout.show(4)
```



## plot 4 normal curves with the paraments:

$$
\begin{eqnarray}
\mu = 10 , \sigma = 4 \\
\mu = 10 , \sigma = 2 \\
\mu = 5 , \sigma = 10 \\
\mu = 5 , \sigma = \frac{1}{2} 
\end{eqnarray}
$$

```{r}
layout(matrix(1:4, nr=2,nc=2))

curve(dnorm(x, mean=10,sd=4),xlim=c(-2, 22))

curve(dnorm(x, mean=10,sd=2),xlim=c(4,16))

curve(dnorm(x, mean=5,sd=10),xlim=c(-25,35))

curve(dnorm(x, mean=5,sd=.5),xlim=c(3,7))
```

## Plot the following regions and probabilities using one graphical interface per plot

$$
\begin{eqnarray}
Y \sim N (0,1), P(Y \ge 2)
\end{eqnarray}
$$

```{r}
curve(dnorm(x, mean=0, sd=1), xlim=c(-3,3))

xcurve=seq(2,5,length=1000)
ycurve=dnorm(xcurve,mean=0,sd=1)

polygon(c(2,xcurve,5),c(0,ycurve,0),col="Red")
area = pnorm(5,mean=0,sd=1)-pnorm(2,mean=0,sd=1)
area=round(area,4)

text(x=2.15, y=0.025, paste("Area = ",area,sep=""))
```

$$
\begin{eqnarray}
Y \sim N (4,2), P(1 \le Y < 5)
\end{eqnarray}
$$
```{r}
curve(dnorm(x, mean=4, sd=2), xlim=c(-2,10))

xcurve=seq(1,5,length=1000)
ycurve=dnorm(xcurve,mean=4,sd=2)

polygon(c(1,xcurve,5),c(0,ycurve,0),col="Red")
area = pnorm(5,mean=4,sd=2)-pnorm(1,mean=4,sd=2)
area=round(area,4)

text(x=3, y=0.10, paste("Area = ",area,sep=""))
```

$$
\begin{eqnarray}
Y \sim N (10,4), P(Y < 10)
\end{eqnarray}
$$
```{r}
curve(dnorm(x, mean=10, sd=4), xlim=c(-2,22))

xcurve=seq(-5,10,length=1000)
ycurve=dnorm(xcurve,mean=10,sd=4)

polygon(c(-5,xcurve,10),c(0,ycurve,0),col="Red")
area = pnorm(10,mean=10,sd=4)-pnorm(-5,mean=10,sd=4)
area=round(area,4)

text(x=5, y=0.03, paste("Area = ",area,sep=""))
```

$$
\begin{eqnarray}
Y \sim N (-2,\frac{1}{2}), P(-3 < Y \le -2)
\end{eqnarray}
$$

```{r}
curve(dnorm(x, mean=-2, sd=0.5), xlim=c(-4,0))

xcurve=seq(-3,-2,length=1000)
ycurve=dnorm(xcurve,mean=-2,sd=0.5)

polygon(c(-3,xcurve,-2),c(0,ycurve,0),col="Red")
area = pnorm(-3,mean=-2,sd=0.5)-pnorm(-2,mean=-2,sd=0.5)
area=round(area,4)

text(x=-2.5, y=0.4, paste("Area = ",abs(area),sep=""))
```

# Task 3

## Plot the following three plots on one plotting surface with overlay

$$
\begin{eqnarray}
Y \sim Gamma (shape = 1, scale = 1) \\
Y \sim Gamma (shape = 3, scale = 1) \\
Y \sim Gamma (shape = 5, scale = 1) 
\end{eqnarray}
$$

```{r}
curve(dgamma(x,shape=1,scale=1),xlim=c(0,10),ylim=c(0,1),col="Maroon", lwd=2, ylab="Gamma Density", main="beta=1")
text(x=1.2,y=0.8,paste("alpha=",1))

curve(dgamma(x,shape=3,scale=1),xlim=c(0,10),ylim=c(0,1),col="Green", add=TRUE, lwd=2)
text(x=2.3,y=0.35,paste("alpha=",3))

curve(dgamma(x,shape=5,scale=1),xlim=c(0,10),ylim=c(0,1),col="Orange", add=TRUE, lwd=2)
text(x=4.5,y=0.25,paste("alpha=",5))
```

$$
\begin{eqnarray}
Y \sim Gamma (shape = 3, scale = 2), P(2<Y<5)
\end{eqnarray}
$$

```{r}
curve(dgamma(x,shape=3,scale=2), xlim=c(0,10), ylim=c(0,0.3), col="Black", lwd=2, ylab="Gamma Density", xlab="Y", main="Gamma Distribution; Shpae = 3; Scale = 2")

xgam1 = seq(2,5,length=1000)
ygam1 = dgamma(xgam1, shape=3, scale=2)
polygon(c(2,xgam1,5), c(0,ygam1,0), col="Dark Slate Gray 2")

gprob1 = pgamma(5,shape=3,scale=2)-pgamma(2,shape=3,scale=2)
gprob1=round(gprob1,4)
text(x=3.2,y=0.17,paste("P(2<Y<5)=", gprob1, sep=""))
```

$$
\begin{eqnarray}
Y \sim Gamma (shape = 6, scale = 3), P(1\le Y\le4)
\end{eqnarray}
$$

```{r}
curve(dgamma(x,shape=6,scale=3), xlim=c(0,5), ylim=c(0,0.005), col="Black", lwd=2, ylab="Gamma Density", xlab="Y", main="Gamma Distribution; Shpae = 6; Scale = 3")

xgam1 = seq(1,4,length=1000)
ygam1 = dgamma(xgam1, shape=6, scale=3)
polygon(c(1,xgam1,4), c(0,ygam1,0), col="Dark Slate Gray 2")

gprob1 = pgamma(4,shape=6,scale=3)-pgamma(1,shape=6,scale=3)
gprob1=round(gprob1,4)
text(x=2,y=0.0037,paste("P(1 <= Y <= 4)=", gprob1, sep=""))
```

$$
\begin{eqnarray}
Y \sim Gamma (shape = 2, scale = 4), P(3\le Y<6)
\end{eqnarray}
$$
```{r}
curve(dgamma(x,shape=2,scale=4), xlim=c(0,8), ylim=c(0,0.15), col="Black", lwd=2, ylab="Gamma Density", xlab="Y", main="Gamma Distribution; Shpae = 2; Scale = 4")

xgam1 = seq(3,6,length=1000)
ygam1 = dgamma(xgam1, shape=2, scale=4)
polygon(c(3,xgam1,6), c(0,ygam1,0), col="Dark Slate Gray 2")

gprob1 = pgamma(6,shape=2,scale=4)-pgamma(3,shape=2,scale=4)
gprob1=round(gprob1,4)
text(x=4.5,y=0.05,paste("P(3 <= Y < 6)=", gprob1, sep=""))
```

# Task 4

## use layout() and beak up the 4 graphical interface for chi-square distribution plot
$$
\begin{eqnarray}
Y \sim chisq (df=1) \\
Y \sim chisq (df=2) \\
Y \sim chisq (df=4) \\
Y \sim chisq (df=20) 
\end{eqnarray}
$$
```{r}
layout(matrix(1:4, nr=2,nc=2))

curve(dchisq(x, df=1),xlim=c(0, 10), lwd=2, xlab="Y", ylab="Chi-Square Density", main="Degrees of Freedom: 1")

curve(dchisq(x, df=2),xlim=c(0, 10), lwd=2, xlab="Y", ylab="Chi-Square Density", main="Degrees of Freedom: 1")

curve(dchisq(x, df=4),xlim=c(0, 10), lwd=2, xlab="Y", ylab="Chi-Square Density", main="Degrees of Freedom: 1")

curve(dchisq(x, df=20),xlim=c(0, 50), lwd=2, xlab="Y", ylab="Chi-Square Density", main="Degrees of Freedom: 1")
```

## Plot the following regions and probabilities in R on separate plotting surfaces
$$
\begin{eqnarray}
Y \sim chisq (df=2), P(2 \le Y \le 4) \\
Y \sim chisq (df=3), P(3 \le Y \le 5) \\
Y \sim chisq (df=20), P(10 < Y \le 21) 
\end{eqnarray}
$$

```{r}
curve(dchisq(x,df=2), xlim=c(0,5), ylim=c(0,0.5), col="Black", lwd=2, ylab="Chi-square density", xlab="Y", main="Chi-Square Distribution; df=2")

xchi = seq(2,4,length=1000)
ychi = dchisq(xchi, df=2)
polygon(c(2,xchi,4), c(0,ychi,0), col="Dark Slate Gray 2")

cprob1 = pchisq(4,df=2)-pchisq(2,df=2)
cprob1=round(cprob1,4)
text(x=3,y=0.3,paste("P(2 <= Y <= 4)=", cprob1, sep=""))
```

```{r}
curve(dchisq(x,df=3), xlim=c(0,10), ylim=c(0,0.5), col="Black", lwd=2, ylab="Chi-square density", xlab="Y", main="Chi-Square Distribution; df=3")

xchi = seq(3,5,length=1000)
ychi = dchisq(xchi, df=3)
polygon(c(3,xchi,5), c(0,ychi,0), col="Dark Slate Gray 2")

cprob1 = pchisq(5,df=3)-pchisq(3,df=3)
cprob1=round(cprob1,4)
text(x=3,y=0.3,paste("P(3 <= Y <= 5)=", cprob1, sep=""))
```

```{r}
curve(dchisq(x,df=20), xlim=c(0,50), ylim=c(0,0.075), col="Black", lwd=2, ylab="Chi-square density", xlab="Y", main="Chi-Square Distribution; df=20")

xchi = seq(10,21,length=1000)
ychi = dchisq(xchi, df=20)
polygon(c(10,xchi,21), c(0,ychi,0), col="Dark Slate Gray 2")

cprob1 = pchisq(21,df=20)-pchisq(10,df=20)
cprob1=round(cprob1,4)
text(x=20,y=0.03,paste("P(10 < Y <= 21)=", cprob1, sep=""))
```

# Task 5

## use layout() and plot 4 weibull plots with any shape and scale 

$$
\begin{eqnarray}
Y \sim Weibull (shape = 3, scale = 1) \\
Y \sim Weibull (shape = 3, scale = 2) \\
Y \sim Weibull (shape = 5, scale = 1) \\
Y \sim Weibull (shape = 5, scale = 2)
\end{eqnarray}
$$

```{r}
layout(matrix(1:4, nr=2,nc=2))
curve(dweibull(x, shape=3, scale=1), xlim=c(0,5), lwd=2, xlab="Y", ylab="weibull density")
curve(dweibull(x, shape=3, scale=2), xlim=c(0,5), lwd=2, xlab="Y", ylab="weibull density")
curve(dweibull(x, shape=5, scale=1), xlim=c(0,5), lwd=2, xlab="Y", ylab="weibull density")
curve(dweibull(x, shape=5, scale=2), xlim=c(0,5), lwd=2, xlab="Y", ylab="weibull density")
```

## Calculate any three areas and probabilites using weibull

$$
\begin{eqnarray}
Y \sim Weibull (shape = 3, scale = 1), P(0 \le Y \le 1) \\
Y \sim Weibull (shape = 3, scale = 2), P(0 \le Y \le 1) \\
Y \sim Weibull (shape = 3, scale = 5), P(0 \le Y \le 3) 
\end{eqnarray}
$$

```{r}
curve(dweibull(x,shape=3,scale=1), xlim=c(0,5), col="Black", lwd=2, ylab="Weibull Density", xlab="Y", main="Weibull Distribution; Shape = 3; Scale = 1")

xwei = seq(0,1,length=1000)
ywei = dweibull(xwei, shape=3, scale=1)
polygon(c(0,xwei,1), c(0,ywei,0), col="Dark Slate Gray 2")

wprob1 = pweibull(1,shape=3,scale=1)-pweibull(0,shape=3,scale=1)
wprob1=round(wprob1,4)
text(x=2,y=0.5,paste("P(0 <= Y <= 1)=", wprob1, sep=""))
```

```{r}
curve(dweibull(x,shape=3,scale=2), xlim=c(0,5), col="Black", lwd=2, ylab="Weibull Density", xlab="Y", main="Weibull Distribution; Shape = 3; Scale = 2")

xwei = seq(0,1,length=1000)
ywei = dweibull(xwei, shape=3, scale=2)
polygon(c(0,xwei,1), c(0,ywei,0), col="Dark Slate Gray 2")

wprob1 = pweibull(1,shape=3,scale=2)-pweibull(0,shape=3,scale=2)
wprob1=round(wprob1,4)
text(x=2,y=0.5,paste("P(0 <= Y <= 1)=", wprob1, sep=""))
```

```{r}
curve(dweibull(x,shape=3,scale=5), xlim=c(0,5), col="Black", lwd=2, ylab="Weibull Density", xlab="Y", main="Weibull Distribution; Shape = 3; Scale = 5")

xwei = seq(0,3,length=1000)
ywei = dweibull(xwei, shape=3, scale=5)
polygon(c(0,xwei,3), c(0,ywei,0), col="Dark Slate Gray 2")

wprob1 = pweibull(3,shape=3,scale=5)-pweibull(0,shape=3,scale=5)
wprob1=round(wprob1,4)
text(x=2,y=0.10,paste("P(0 <= Y <= 3)=", wprob1, sep=""))
```

# Task 6

## repeat task 5 but with beta distribution

$$
\begin{eqnarray}
Y \sim Beta (\alpha = 2, \beta = 1) \\
Y \sim Beta (\alpha = 2, \beta = 2) \\
Y \sim Beta (\alpha = 4, \beta = 1) \\
Y \sim Beta (\alpha = 4, \beta = 2) 
\end{eqnarray}
$$

```{r}
layout(matrix(1:4, nr=2,nc=2))
curve(dbeta(x,2,1), lwd=2, xlim=c(0,2), xlab="Y", ylab="beta density")
curve(dbeta(x,2,2), lwd=2, xlim=c(0,2), xlab="Y", ylab="beta density")
curve(dbeta(x,4,1), lwd=2, xlim=c(0,2), xlab="Y", ylab="beta density")
curve(dbeta(x,4,2), lwd=2, xlim=c(0,2), xlab="Y", ylab="beta density")
```

## beta distribution with P(0 <= Y <= 1)

$$
\begin{eqnarray}
Y \sim Beta (\alpha = 2, \beta = 1), P(0 \le Y \le 1) \\
Y \sim Beta (\alpha = 2, \beta = 2), P(0 \le Y \le 1) \\
Y \sim Beta (\alpha = 4, \beta = 1), P(0 \le Y \le 1) 
\end{eqnarray}
$$

```{r}
curve(dbeta(x,2,1), xlim=c(0,5), col="Black", lwd=2, ylab="Beta Density", xlab="Y", main="Beta Distribution; Alpha = 2; Beta = 1")

xbeta = seq(0,1,length=1000)
ybeta = dbeta(xbeta,2,1)
polygon(c(0,xbeta,1), c(0,ybeta,0), col="Dark Slate Gray 2")

bprob1 = pbeta(1,2,1)-pbeta(0,2,1)
bprob1=round(bprob1,4)
text(x=3,y=1,paste("P(0 <= Y <= 1)=", bprob1, sep=""))
```

```{r}
curve(dbeta(x,2,2), xlim=c(0,5), col="Black", lwd=2, ylab="Beta Density", xlab="Y", main="Beta Distribution; Alpha = 2; Beta = 2")

xbeta = seq(0,1,length=1000)
ybeta = dbeta(xbeta,2,2)
polygon(c(0,xbeta,1), c(0,ybeta,0), col="Dark Slate Gray 2")

bprob1 = pbeta(1,2,2)-pbeta(0,2,2)
bprob1=round(bprob1,4)
text(x=3,y=1,paste("P(0 <= Y <= 1)=", bprob1, sep=""))
```

```{r}
curve(dbeta(x,4,1), xlim=c(0,5), col="Black", lwd=2, ylab="Beta Density", xlab="Y", main="Beta Distribution; Alpha = 4; Beta = 1")

xbeta = seq(0,1,length=1000)
ybeta = dbeta(xbeta,4,1)
polygon(c(0,xbeta,1), c(0,ybeta,0), col="Dark Slate Gray 2")

bprob1 = pbeta(1,4,1)-pbeta(0,4,1)
bprob1=round(bprob1,4)
text(x=3,y=1,paste("P(0 <= Y <= 1)=", bprob1, sep=""))
```

# Task 7

## run function from package

```{r}
library(PATEL2021)
PATEL2021::myncurve(mu=10,sigma=5,a=6)
```

